Naomi model workflow

### 2022-10-17 src/example_naomi/naomi.Rmd
Upload start on Naomi vignette

```{r}
naomi_mf <- naomi_model_frame(
  area_merged,
  pop_agesex,
  spec,
  scope = scope,
  level = level,
  calendar_quarter_t1,
  calendar_quarter_t2,
  calendar_quarter_t3
)
```

```{r}
naomi_data <- select_naomi_data(
  naomi_mf,
  survey_hiv_indicators,
  anc_testing,
  art_number,
  prev_survey_ids,
  artcov_survey_ids,
  recent_survey_ids,
  vls_survey_ids,
  artnum_calendar_quarter_t1,
  artnum_calendar_quarter_t2,
  anc_prevalence_year1,
  anc_prevalence_year2,
  anc_art_coverage_year1,
  anc_art_coverage_year2
)
```

@@

```{r}
fit <- fit_tmb(tmb_inputs)
```

```{r}
outputs <- output_package(fit, naomi_mf)
names(outputs)
```

```{r}
outputs$indicators %>%
  dplyr::filter(
    indicator == "prevalence",  # HIV prevalence
    age_group == "Y015_049"   # Age group 15-49
  ) %>%
  head()
```

```{r}
add_output_labels(outputs) %>%
  dplyr::filter(
    indicator == "prevalence",  # HIV prevalence
    age_group == "Y015_049"   # Age group 15-49
  ) %>%
  head()
```

```{r}
system.time(fit <- sample_tmb(fit))
```

```{r}
system.time(outputs <- output_package(fit, naomi_mf))

>>>>

```{r eval=FALSE}
naomi_mf <- naomi_model_frame(
  area_merged,
  pop_agesex,
  spec,
  scope = scope,
  level = level,
  calendar_quarter_t1,
  calendar_quarter_t2,
  calendar_quarter_t3
)
```

```{r eval=FALSE}
naomi_data <- select_naomi_data(
  naomi_mf,
  survey_hiv_indicators,
  anc_testing,
  art_number,
  prev_survey_ids,
  artcov_survey_ids,
  recent_survey_ids,
  vls_survey_ids,
  artnum_calendar_quarter_t1,
  artnum_calendar_quarter_t2,
  anc_prevalence_year1,
  anc_prevalence_year2,
  anc_art_coverage_year1,
  anc_art_coverage_year2
)
```

@@

```{r eval=FALSE}
fit <- fit_tmb(tmb_inputs)
```

```{r eval=FALSE}
outputs <- output_package(fit, naomi_mf)
names(outputs)
```

```{r eval=FALSE}
outputs$indicators %>%
  dplyr::filter(
    indicator == "prevalence",  # HIV prevalence
    age_group == "Y015_049"   # Age group 15-49
  ) %>%
  head()
```

```{r eval=FALSE}
add_output_labels(outputs) %>%
  dplyr::filter(
    indicator == "prevalence",  # HIV prevalence
    age_group == "Y015_049"   # Age group 15-49
  ) %>%
  head()
```

```{r eval=FALSE}
system.time(fit <- sample_tmb(fit))
```

```{r eval=FALSE}
system.time(outputs <- output_package(fit, naomi_mf))
